Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex

when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}). Recently there has been some success in tackling uncertainty quantification

>>>>

when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{mccloskey1989catastrophic}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}). Recently there has been some success in tackling uncertainty quantification
